### 2017-02-27 Writing/draft.tex
Draft equations proofs

\subsubsection{Characters difference (CD)}
\begin{equation}
    CD_{(x,y)} = 1 - \left(\frac{\abs*{\frac{\abs*{\sum_{i}^{n}(x_{i} - y_{i})}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right)
\end{equation}

@@

% mcmc nruns=2 Nchains=6 ngen=100000000 samplefreq=200 printfreq=2000 diagnfreq=10000 Stoprule=YES stopval=0.01 mcmcdiagn=YES file=150t_100c_0304_maxi;
% sump Filename=150t_100c_0304_maxi Relburnin=YES Burninfrac=0.25;
% sumt Filename=150t_100c_0304_maxi Relburnin=YES Burninfrac=0.25;

@@

% Suggested reviewers:
%- Liliana Davalos

>>>>

\subsubsection{Characters difference (CD)}
\begin{equation}
    CD_{(x,y)} = 1 - \left(\frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i} - y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right)
\end{equation}

@@

% mcmc nruns=2 Nchains=6 ngen=1000000000 samplefreq=200 printfreq=2000 diagnfreq=10000 Stoprule=YES stopval=0.01 mcmcdiagn=YES file=150t_100c_0304_maxi;
% sump Filename=150t_100c_0304_maxi Relburnin=YES Burninfrac=0.25;
% sumt Filename=150t_100c_0304_maxi Relburnin=YES Burninfrac=0.25;

@@

% Suggested reviewers:
%- Liliana Davalos for MPE

\section{Appendix A - Character difference}

The Character Difference ($CD$) metric is a distance $d: CD \times CD \rightarrow [0;\infty)$ with any character $x$, $y$ and $z$ $\in CD$ if an only if the followings are satisfied:

\begin{equation}
    \label{Positivity}
    CD_{(x,y)} \geq 0
\end{equation}
\begin{equation}
    \label{Identity}
    CD_{(x,y)} = 0 \Leftrightarrow x = y
\end{equation}
\begin{equation}
    \label{Equality}
    CD_{x,y} = CD_{y,x}
\end{equation}
\begin{equation}
    \label{Subadditivity}
    CD_{(x,y)} \leq CD_{(x,z)} + CD_{(z,y)}
\end{equation}

\subsection{Character difference positivity}

For any $n \in [1;\infty)$ and $x_{n}$ and $y_{n} \in (0,1)$ (because the difference between character states is considered as Fitch-like, i.e. the difference between two characters states \texttt{0} and \texttt{8} is equal to $1$ and the difference between two identical character states is equal to $0$:

\begin{equation}
    \label{positive_demo}
    \begin{gathered}
    0 \leq  \abs{x_{n}-y_{n}} \leq 1\\
    0 \leq  \sum_{i=1}^{n}\abs{x_{i}-y_{i}} \leq n\\
    0 \leq  \frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n} \leq 1\\
    0 \leq  \abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} \leq \frac{1}{2}\\
    0 \leq  \frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}} \leq 1\\
    0 \leq  1 - \left(\frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right) \leq 1\\
    \end{gathered}
\end{equation}

Thus equation \ref{Positivity} is true.

\subsection{Character difference identity}

For any $n \in [1;\infty)$ and $x_{n} = y_{n}$ then:
%TG: Is that valid for a demonstration?
\begin{equation}
    \label{identitydemo}
    \begin{aligned}
    \abs{x_{n}-y_{n}} &= 0\\
    \sum_{i}^{n}\abs{x_{i}-y_{i}} &= 0\\
    \frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n} &= 0\\
    \abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} &= 0\\
    \frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}} &= 0\\
    1 - \left(\frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right) &= 0\\
    \end{aligned}
\end{equation}

Thus equation \ref{Identity} is true.

\subsection{Character difference equality}

For any $n \in [1;\infty)$ and $x_{n}$ and $y_{n} \in (0,1)$, similarly to equation \ref{positive_demo}:

\begin{equation}
    \label{equality_demo}
    \begin{aligned}
    \abs{x_{n}-y_{n}} &= \abs{y_{n}-x_{n}}\\
    \sum_{i}^{n}\abs{x_{i}-y_{i}} &= \sum_{i}^{n}\abs{y_{i}-x_{i}}\\
    \frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n} &= \frac{\sum_{i}^{n}\abs{y_{i}-x_{i}}}{n}\\
    \abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} &= \abs*{\frac{\sum_{i}^{n}\abs{y_{i}-x_{i}}}{n}-\frac{1}{2}}\\
    \frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}} &= \frac{\abs*{\frac{\sum_{i}^{n}\abs{y_{i}-x_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\\
    1 - \left(\frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right) &= 1 - \left(\frac{\abs*{\frac{\sum_{i}^{n}\abs{y_{i}-x_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right)\\
    \end{aligned}
\end{equation}

Thus equation \ref{Equality} is true.

\subsection{Character difference subadditivity}

As described in equations \ref{Positivity}, \ref{Identity} and \ref{Equality},

\begin{equation}
    \label{subadditivity_demo}
    \begin{aligned}
    &0\leq CD_{x,z} \leq 1\\
    &\text{and}\\
    &0\leq CD_{z,y} \leq 1\\
    &\text{thus}\\
    &0\leq CD_{x,z} + CD_{z,y}  \leq 2\\
    \end{aligned}
\end{equation}

\subsubsection{Case 1}
If $CD_{x,z} = 0$, then, following \ref{Identity}:

\begin{equation}
    \label{subadditivity_demo_case1}
    \begin{aligned}
    &CD_{x,z} = CD_{z,y} = CD_{x,y}\\
    &\text{then}\\
    &CD_{x,y} \leq CD_{x,z} + CD_{z,y}\\
    \end{aligned}
\end{equation}

\subsubsection{Case 2}
If $CD_{x,z} > 0$, then:

\begin{equation}
    \label{subadditivity_demo_case2}
    \begin{aligned}
    &CD_{x,z} = CD_{z,y} = CD_{x,y}\\
    &\text{then}\\
    &CD_{x,y} \leq CD_{x,z} + CD_{z,y}\\
    \end{aligned}
\end{equation}

% \subsubsection{Character difference metric is ontological (identity of indiscernibles)}

% \begin{equation}
%     \label{CDnull}
%     CD_{(x,y)} = 0 \Leftrightarrow x = y
% \end{equation}
% This is because of equation \ref{equality}; in fact $x$ and $y$ is actually expressed in terms of phylogenetic information per character (i.e. normalised for character state token).

% \subsubsection{Character difference metric is sub-additive (triangle inequality)}

% \begin{equation}
%     \label{subadditive}
%     CD_{(x,y)} \leq CD_{(x,z)} + CD_{(z,y)}
% \end{equation}
% Following equations \ref{CDpositive}, \ref{equality}, \ref{CDnull}.

% Thus:

% \begin{equation}
%     d: \frac{\abs*{\sum_{i}^{n}(x_{i} - y_{i})}{n} \rightarrow [0;1]
% \end{equation}

% Thus:

% \begin{equation}
%     d: \frac{\sum_{i}^{n}(x_{i} - y_{i})}{n} \rightarrow [0;1]
% \end{equation}
